Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-13 mtjournal.tex
whitespace and linewrap cleanup

We may evaluate automatic MT measures in a variety of ways. Some
\cite{banerjee05meteor,liu05syntaxformteval,owczarzak07labelleddepseval}
have evaluated their success by comparing the measure to human
judgments of fluency and adequacy.  In other work,
e.g. \inlinecite{snover06ter}, measures are evaluated by comparison to
human-targeted TER (HTER), a distance to a human-revised reference
that uses wording closer to the MT system choices (keeping the
original meaning) that is intended to measure the post-editing work
required after translation.  In this paper, we explore both kinds of
evaluation.

@@

\item[Size of $n$-best list.] Although the parser can generate considerably more,
  we consider $n$-best lists  of size 1 and of size 50.
\item[Confidence of $n$-best list.] An expectation requires a probability
  distribution over the $n$-best list, and we consider three options:
  uniform, the parser probabilities, and a flattened version of the
  parser probabilities such that $\tilde{p}(x) =

@@

    \inlinecite{owczarzak07labelleddepseval} report no use of parse weights,
    \textbf{d\_50} and \textbf{d\_50\_var} may be using a sum of
    counts over the 50-best list rather than expected-counts over a

@@

talk about why EN is < EDPM (is it?)

>>>>

We may evaluate automatic MT measures in a variety of ways. Some
\cite{banerjee05meteor,liu05syntaxformteval,owczarzak07labelleddepseval}
have evaluated their success by comparing the measure to human
judgments of fluency and adequacy.  In other work, e.g.\
\inlinecite{snover06ter}, measures are evaluated by comparison to
human-targeted TER (HTER), a distance to a human-revised reference
that uses wording closer to the MT system choices (keeping the
original meaning) that is intended to measure the post-editing work
required after translation.  In this paper, we explore both kinds of
evaluation.

@@

\item[Size of $n$-best list.] Although the parser can generate
  considerably more, we consider $n$-best lists of size 1 and of size
  50.
\item[Confidence of $n$-best list.] An expectation requires a
  probability distribution over the $n$-best list, and we consider
  three options: uniform, the parser probabilities, and a flattened
  version of the parser probabilities such that $\tilde{p}(x) =

@@

    \inlinecite{owczarzak07labelleddepseval} report no use of parse
    weights, \textbf{d\_50} and \textbf{d\_50\_var} may be using a sum
    of counts over the 50-best list rather than expected-counts over a

@@

talk about why EN is $<$ EDPM (is it?)
